Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-08-17 nir_companions.tex
Reorder citations

\section*{Acknowledgements}
This work was supported by Funda\c{c}\~ao para a Ci\^encia e a Tecnologia (FCT) (Portugal) research grants through national funds and from FEDER through COMPETE2020 by the following grants: UID/FIS/04434/2013, \& POCI--01--0145-FEDER--007672,\& PTDC/FIS-AST/1526/2014, \& POCI--01--0145-FEDER--016886, \& PTDC/FIS-AST/7073/2014, \& POCI-01-0145-FEDER-016880, \& POCI-01-0145-FEDER-032113.
J.J.N. acknowledges support from FCT though the PhD::Space fellowship PD/BD/52700/2014.
P.F., N.C.S. acknowledge support from FCT through Investigador FCT contracts IF/01037/2013CP1191/CT0001, \& IF/01312/2014/CP1215/CT0004, \& IF/00169/2012/CP0150/CT0002, \& IF/00028/2014/CP1215/CT0002.
This work made use of \textsc{PyAstronomy}\footnote{Available at \href{https://pyastronomy.readthedocs.io}{https://pyastronomy.readthedocs.io}} and many other open source and under-credited software packages numpy, scipy, astropy, Starfish to name a few.
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France.

>>>>

\section*{Acknowledgements}
This work was supported by Funda\c{c}\~ao para a Ci\^encia e a Tecnologia (FCT) (Portugal) research grants through national funds and from FEDER through COMPETE2020 by the following grants: UID/FIS/04434/2013, \&  PTDC/FIS-AST/1526/2014, \& PTDC/FIS-AST/7073/2014, \& POCI--01--0145-FEDER--016886, \& POCI--01--0145-FEDER--007672, \& POCI-01-0145-FEDER-016880, \& POCI-01-0145-FEDER-032113.
J.J.N. acknowledges support from FCT though the PhD::Space fellowship PD/BD/52700/2014.
P.F., N.C.S. acknowledge support from FCT through Investigador FCT contracts IF/01037/2013CP1191/CT0001, \& IF/00169/2012/CP0150/CT0002, \& IF/00028/2014/CP1215/CT0002, \& IF/01312/2014/CP1215/CT0004.
This work made use of \textsc{PyAstronomy}\footnote{Available at \href{https://pyastronomy.readthedocs.io}{https://pyastronomy.readthedocs.io}} and many other open source and under-credited software packages numpy, scipy, astropy, Starfish to name a few.
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France.
